15 March..
attempt to find the trouble in the new model..
At the moment we think that the trouble likely is in the ellipse generation functions, though we are not precisely sure as it might also sit in some of the estimation with the sf package.

Actually it is more likely as we can have a problem in the distances, estimated by the sf...
the problem is that we do everything within the loop, so we have to alternate loop and to save individual results immediately after simulation..
All the outcomes of the simulation should be qite similar then..



---
title: "Supplementary Code, Simulation"
author: "Julia Karagicheva and Eldar Rakhimberdiev"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Supplement to: Karagicheva et al. "The need to account for Argos Doppler errors when estimating habitat use from Argos Doppler locations: evidence and solution." 

Depends:  R (>= 3.2.0)

Date: 2023-02-27

Description: This R code uses simulated Argos locations to demonstrate the performance of habitat selection analyses, using 1) raw Argos locations; 2.) SSM-improved Argos locations; and 3.) the SSM-derived 'most likely habitat' approach. Simulated locations are created using GPS tracks of Black-tailed Godwits. 


### Load required R packages
```{r, eval=FALSE}
library(dplyr)
library(tidyr)
library(sp)
library(sf)
library(lubridate)
library(raster)
library(ggplot2)
library('mvnfast')
library('mvtnorm')
library(tidyverse)
library(ctmm)
library('Rcpp')
library(ggpubr)
```

### Ellipse functions

Necessary functions for simulating Argos location error, written by Eldar Rakhimberdiev.
```{r, eval=FALSE}
ellipse_params<-function(semi_major, semi_minor, orientation, res.mat=FALSE) {
   # original equations by McClintock MEE 2015
   M_t=semi_major
   m_t=semi_minor
   c_t=orientation*pi/180
   sigma_sq_x_t=(((M_t)*sin(c_t))^2 + ((m_t)*cos(c_t))^2)/2
   sigma_sq_y_t=(((M_t)*cos(c_t))^2 + ((m_t)*sin(c_t))^2)/2
   sigma_xy_t=(M_t^2-m_t^2)*cos(c_t)*sin(c_t)/2
   VCmat<-matrix(c(sigma_sq_x_t, sigma_xy_t, sigma_xy_t, sigma_sq_y_t), nrow=2)
   if (!res.mat) {
      Res<-list(Mu=c(0,0), VCmat=VCmat)
   } else {
      Res<-cbind(sigma_sq_x_t, sigma_sq_y_t, sigma_xy_t)
   }
}

long2UTM <- function(long) {
    (floor((long + 180)/6) %% 60) + 1
}

get_grid_dmvn<-function(data_row, Grid) {
    VCmat_cur<-ellipse_params(data_row$argos_semi_major, data_row$argos_semi_minor, data_row$argos_orientation)$VCmat
	Mean_cur<-c(data_row$longUTM,data_row$latUTM)
	
	if (data_row$argos_semi_major == 0| data_row$argos_semi_minor==0) {
	Z<-rep(0,nrow(Grid))
	} else {
    Z<-try(apply(Grid, 1, FUN=function(x) 
			       mvnfast::dmvn(c(x[1], x[2]) ,mu=Mean_cur,
				        sigma=VCmat_cur)))
	if (class(Z)=='try-error') {
	save(data_row, file='Data_row_tmp.RData')
	Z<-apply(Grid, 1, FUN=function(x) 
	               mvtnorm::dmvnorm(c(x[1], x[2]), mean = Mean_cur, 
				   sigma = VCmat_cur))
	} 	
    }	
	return(Z)
}

get_grid_dmvn<-compiler::cmpfun(get_grid_dmvn)

get_ellipse_random_points<-function(n, data_row) {
    VCmat_cur<-ellipse_params(data_row$argos_semi_major, data_row$argos_semi_minor, data_row$argos_orientation)$VCmat
	Mean_cur<-c(data_row$longUTM,data_row$latUTM)
	if (data_row$argos_semi_major == 0| data_row$argos_semi_minor==0) {
       Points<-matrix(NA, nrow=n, ncol=2)
	} else {
       Points<-try(mvnfast::rmvn(n=n,mu=Mean_cur, sigma=VCmat_cur))
	   if (class(Points)[1]=='try-error') {
	     save(data_row, file='Data_row_tmp.RData')
	     Points<-mvtnorm::rmvnorm(n=n, mean = Mean_cur, sigma = VCmat_cur)
	   } 	
    }	
	return(Points)
}
```


### Load Data 

Load the habitat map.

```{r, eval=FALSE}
Cur_sf <- st_read('.\\Ruth_map\\Std_Dev_polygons_rdnew.shp')
Cur_sf <- Cur_sf %>% sf:::select.sf(habitat)
```

To distinguish between points falling beyond the map range and those falling on the 'not assigned' habitat within the map, create a 50 meter buffer.  
```{r, eval=FALSE}
Buffer_50_st <- Cur_sf %>% 
  st_union() %>% 
  st_buffer(dist=50, capStyle="ROUND", joinStyle="ROUND", mitreLimit=1.0) %>% 
  st_as_sf()

Buffer_50_st$in_buffer <- 1
```

Load Argos (PTT) tracks of 14 individual Black-tailed Godwits. 
```{r, eval=FALSE}
act_god <- read.csv(file='Active Godwits_08_12_2020.csv',stringsAsFactors=F)
```

Load GPS track of one individual Black-tailed Godwit.
```{r, eval=FALSE}
uva2002 <- read.csv(file='UVA_TRACKER2002.csv',stringsAsFactors=F)  %>%
subset(select=c('device_info_serial', 'date_time', 'latitude', 'longitude'))

# Format columns
uva2002$datetime <- as.POSIXct(uva2002$date_time, format = "%m/%d/%Y %H:%M", tz = "UTC") 
uva2002$Date <- as.POSIXct(uva2002$date_time, format = "%m/%d/%Y", tz = "UTC") 
uva2002$fixID<-rownames(uva2002)

# Transform from longlat to UTM
Cur_zone<-31

uva2002_SP_sf_UTM<-st_as_sf(x=uva2002, coords=c('longitude', 'latitude'),  
                            crs = CRS("+init=epsg:4326"), remove=FALSE) %>%
  st_transform( crs=CRS(paste0('+proj=utm +zone=',Cur_zone, ' datum=WGS84')))

uva2002_SP_sf_UTM[c('longUTM', 'latUTM')]<-st_coordinates(uva2002_SP_sf_UTM)

uva2002_SP_sf_RDn<-st_transform(uva2002_SP_sf_UTM, crs(Cur_sf))

# Extract only locations in the Netherlands
uva2002_SP_RDn_NL_habitat<-uva2002_SP_sf_UTM %>% 
                           filter(latitude>52.8) %>% 
                           filter(datetime < as.POSIXct("2014-01-01 UTC")) %>%
                           st_transform(crs(Cur_sf))

# Format data
gps_samp <- uva2002_SP_RDn_NL_habitat %>% 
  sf:::select.sf(gps_longUTM=longUTM, gps_latUTM=latUTM, 
                 fixID=fixID, datetime=datetime)
 
```

### Run Simulation 

Sample habitat at 'true' GPS locations. 
```{r, eval=FALSE} 
input_gps_coords <- st_as_sf(x=gps_samp, 
                           coords=c('gps_longUTM', 'gps_latUTM'),
                           rs=CRS(paste0('+proj=utm +zone=',Cur_zone))) %>%
  st_transform(crs(Cur_sf))

gps_habitat_NA_within <- input_gps_coords %>% 
  st_join(Cur_sf, join = st_within) %>% 
  st_join(Buffer_50_st, join = st_within)

# Identify 'not assigned' habitat   
gps_habitat_NA_within$habitat[is.na(gps_habitat_NA_within$habitat) & !is.na(gps_habitat_NA_within$in_buffer)] <- 'not_assigned'
   
gps_RDnew<-as.data.frame(st_coordinates(input_gps_coords))
names(gps_RDnew)<-c('gps_RDn_lon','gps_RDn_lat')
```

Simulate an Argos track by scattering points within an Argos error ellipse.
```{r, eval=FALSE}
simulate_arg_track <- function(x) {
  data_row<-as.data.frame(x)
  arg_sim_track<-data.frame(get_ellipse_random_points(1,data_row))
  return(arg_sim_track)
}
```

Prepare the Argos error ellipse data.
```{r, eval=FALSE}
# Format date-time 
act_god$datetime <- as.POSIXct(act_god$timestamp, 
                               format = "%Y-%m-%d %H:%M:%S", 
                               tz = "UTC")

# Rename key columns
act_god$argos_semi_major <- act_god$argos.semi.major
act_god$argos_semi_minor <- act_god$argos.semi.minor
act_god$argos_orientation <- act_god$argos.orientation

# Select quality fixes
act_god<-act_god[act_god$argos.lc %in% c("1","2","3"),]

# Remove locations outside of the Netherlands 
act_god_noNA <- act_god %>% 
  filter(!is.na(location.long)) %>% 
  filter(argos_semi_major!=0) %>% 
  filter(argos_semi_minor!=0) %>% 
  filter(location.lat>52.8)

# Reproject to CRS of the study area
sf_act_god_noNA <- st_as_sf(x=act_god_noNA,
                            coords=c('location.long','location.lat'),
                            crs=CRS("+init=epsg:4326")) %>% 
      st_transform(crs(Cur_sf))

sf_act_god_noNA_quality_control <- sf_act_god_noNA
```


Run the simulations, using CTMM to fit SSMs, estimate the path 100 times while taking elliptical error into account, and sample the underlying habitat. This function will take some time. Output of each simulation run saves to an .RData file.
```{r, eval=FALSE}
Total_sims<-50
n.simulations=100  

for (j in 31:Total_sims) {
   cat('\r doing', j, 'from ', Total_sims)
   samp <- sample.int(nrow(sf_act_god_noNA_quality_control),nrow(uva2002_SP_RDn_NL_habitat),replace=TRUE)
   arg_samp <- sf_act_god_noNA_quality_control[samp,c('argos_semi_major','argos_semi_minor','argos_orientation')] %>%
   st_drop_geometry
   arg_samp$samp <- samp

   track_gps_arg <- cbind(gps_samp,arg_samp)

   data_frame <- track_gps_arg %>% st_drop_geometry() %>% dplyr::select(longUTM=gps_longUTM,
                                                 latUTM=gps_latUTM,argos_semi_major=argos_semi_major,
                                                 argos_semi_minor=argos_semi_minor,argos_orientation=argos_orientation)

   SP_nosp <- do.call(rbind, apply(data_frame,1, FUN=function(x) simulate_arg_track(as.data.frame(t(x)))))
   
   track_gps_arg[,c('x', 'y')] <- SP_nosp
   
   input <- st_as_sf(x=st_drop_geometry(track_gps_arg), coords=c('x', 'y'), 
                   crs = CRS(paste0('+proj=utm +zone=', Cur_zone))) %>% 
     st_transform( CRS("+init=epsg:4326")) 

   input[, c('location_lon', 'location_lat')] <- input %>% 
     st_coordinates()
   Data_for_ctmm <- input %>% 
     st_drop_geometry() %>% dplyr::select(timestamp=datetime, longitude=location_lon, 
           latitude=location_lat, Argos.semi.major=argos_semi_major,
           Argos.semi.minor=argos_semi_minor, Argos.orientation=argos_orientation) %>%
           mutate(sensor_type='argos-doppler-shift') 
           
   cur_track_ctmm <- as.telemetry(Data_for_ctmm)
   if (FALSE) {
      plot(cur_track_ctmm)
   }
   # Automated guesstimate for calibrated data
   GUESS <- ctmm.guess(cur_track_ctmm,CTMM=ctmm(error=TRUE),interactive=FALSE)

   # Stepwise fitting of movement models -- this takes some time 
   if (TRUE) {
      FIT <- ctmm.select(cur_track_ctmm,GUESS,trace=FALSE,cores=6)
	  
    # If desired, may save the object for further re-use
      #save(FIT, file='FIT_simulation.RData')
   }
  

# Make a brick with three dimensions (coord, time, simID) to store output
sim.brick <- array(NA, c( nrow(cur_track_ctmm), 2, n.simulations))

# Run simulation
Sim_1 <- simulate(FIT, data=cur_track_ctmm, precompute=TRUE, t=cur_track_ctmm$t) 
   for (i in 1:n.simulations) {
      cat('\r', i)
      Sim_1 <- simulate(FIT, data=cur_track_ctmm, 
                        precompute=-1, t=cur_track_ctmm$t) 
      sim.brick[,,i]<- st_as_sf(x=data.frame(ID=1:length(Sim_1@.Data[[2]]),
                                             x=Sim_1@.Data[[2]],
                                             y=Sim_1@.Data[[3]]), coords=c('x', 'y'),  
                                crs = projection(Sim_1))  %>% 
      st_transform(crs('+proj=longlat +datum=WGS84 +no_defs')) %>%
        st_coordinates()
	  }

# Overlay the output with the habitat map
Output.sim<-Data_for_ctmm
attr(Output.sim,"sim.error") <- sim.brick

all_out <- c()
for (i in 1:dim(attr(Output.sim,"sim.error"))[3]) {
      cat('\r', i)

      Sim_SPts <- st_as_sf(x=data.frame(x=attr(Output.sim,"sim.error")[,1,i],
                                        y=attr(Output.sim,"sim.error")[,2,i]),
                           coords=c('x', 'y'),  
                           crs = crs('+proj=longlat +datum=WGS84 +no_defs')) %>%
      st_transform(crs(Cur_sf))
      
				# Remove points outside the area
				overlay_area <- st_join(Sim_SPts, Cur_sf, join = st_within)
				overlay_buffer_sf <- st_join(Sim_SPts, Buffer_50_st, join = st_within)				
				habitat_NA_within <- data.frame(habitat=overlay_area$habitat, in_buffer=overlay_buffer_sf$in_buffer)
				habitat_NA_within$habitat[is.na(habitat_NA_within$habitat) & !is.na(habitat_NA_within$in_buffer)]<-'not_assigned'

	  all_out <- cbind(all_out, habitat_NA_within$habitat)
   }

   Habitat_types <- as.data.frame(t(apply(all_out, 1, FUN=function(x)unlist(table(factor(x,  levels=c('high_change', 'intermediate', 'low_change', 'not_assigned' )), useNA='always')))))
   names(Habitat_types) <- paste0('ctmm_simulation_', as.character(names(Habitat_types)))

   Data_for_ctmm$most.present.habitat_ctmm_sim<-
   apply(Habitat_types, 1, FUN=function(x) c('high_change', 'intermediate', 'low_change','not_assigned')[which.max(x[1:4])])
   input_with_habitats <- cbind(Data_for_ctmm, Habitat_types)  

	overlay_area_argos <- input %>% 
	  st_transform(crs(Cur_sf)) %>% 
	  st_join(Cur_sf, join = st_within)
	overlay_buffer_sf_argos <- input %>% 
	  st_transform(crs(Cur_sf)) %>% 
	  st_join(Buffer_50_st, join = st_within)				
	habitat_NA_within_argos <- data.frame(habitat=overlay_area_argos$habitat, in_buffer=overlay_buffer_sf_argos$in_buffer)
	habitat_NA_within_argos$habitat[is.na(habitat_NA_within_argos$habitat) & !is.na(habitat_NA_within_argos$in_buffer)]<-'not_assigned'
    
   input_with_habitats$habitat_sim_arg_centre <-habitat_NA_within_argos$habitat

  input_with_habitats <- input_with_habitats %>% 
    rename(arg_sim_long=longitude, arg_sim_lat=latitude)

# Predict locations using SSM
   Pred<-predict(FIT, data=cur_track_ctmm,  t=cur_track_ctmm$t) 
   
   Pred_SPts<-st_as_sf(x=data.frame(ID=1:length(Pred@.Data[[2]]),
                                    x=Pred@.Data[[2]], y=Pred@.Data[[3]]),
                       coords=c('x', 'y'),  crs = projection(Pred)) %>% 
      st_transform(crs(Cur_sf))
   
				# Remove points outside the area
				overlay_ctmm_area <- st_join(Pred_SPts, Cur_sf, join = st_within)
				overlay_ctmm_buffer <- st_join(Pred_SPts, Buffer_50_st, join = st_within)				
				ctmm_habitat_NA_within <- data.frame(habitat=overlay_ctmm_area$habitat, in_buffer=overlay_ctmm_buffer$in_buffer)
				ctmm_habitat_NA_within$habitat[is.na(habitat_NA_within$habitat) & !is.na(habitat_NA_within$in_buffer)]<-'not_assigned'
   
   input_with_habitats$ctmm_predicted_habitat<-ctmm_habitat_NA_within$habitat
    
ctmm_pred_coords<-Pred_SPts %>% 
                     st_transform(crs('+proj=longlat +datum=WGS84 +no_defs')) %>%
                     st_coordinates() %>% 
                     as.data.frame()
                     
names(ctmm_pred_coords) <- c('ctmm_pred_longitude', 'ctmm_pred_latitude')
   
   output_with_everything <- cbind(input_with_habitats, ctmm_pred_coords,gps_RDnew)
   
   output_with_everything$gps_habitat <- gps_habitat_NA_within$habitat

   filename<-paste0('Sim_', j, '_output_with_everything_not_assigned_cor_sf_v.2.RData')
   save(output_with_everything, file=filename)
}
```

###Analyse simulated tracks
```{r, eval=FALSE}


#list the files from the directory, where the simulation output was saved
Files<-list.files("D:\\...", 'Sim_')

##FIGURE 5
#Study site with the GPS track of the godwit

clrs<-c('#d95f02','#7570b3','#1b9e77',grey(0.9))
clrs_map<-c('#fc8d62','#8da0cb','#66c2a5')

Cur_sp$habitat_num[Cur_sp$habitat=="high_change"]<-1
Cur_sp$habitat_num[Cur_sp$habitat=="intermediate"]<-2
Cur_sp$habitat_num[Cur_sp$habitat=="low_change"]<-3

output_with_everything_sp<-st_as_sf(x=output_with_everything, coords = c('gps_RDn_lon','gps_RDn_lat'), crs=crs(Cur_sp))

x_coord<-c(158012.8, 158012.8,159000.0,159000.0, 158012.8)
y_coord<-c(549500.0, 548366.0, 548366.0, 549500.0, 549500.0)
xym <- cbind(x_coord, y_coord)
xym
p = Polygon(xym)
ps = Polygons(list(p),1)
sps = SpatialPolygons(list(ps))
###############
st_p<-st_polygon(x=list(xym)) %>% st_sfc(crs=crs(Cur_sp))



plot(st_geometry(Cur_sp), border=grey(0.8),lwd=0.1, col=clrs_map[Cur_sp$habitat_num])
plot(st_geometry(output_with_everything_sp),pch=".",cex=2,col='yellow',add=T)
plot(st_p,add=T ,border='white',lwd=2)
plot(st_geometry(sps),border='white',lwd=2,add=T)


#Make a fragment of the map to show points in details

#Give numbers to the habitat types for each of the approaches

output_with_everything_sp$gps_habitat_num[output_with_everything_sp$gps_habitat=='high_change']<-1
output_with_everything_sp$gps_habitat_num[output_with_everything_sp$gps_habitat=='intermediate']<-2
output_with_everything_sp$gps_habitat_num[output_with_everything_sp$gps_habitat=='low_change']<-3
output_with_everything_sp$gps_habitat_num[output_with_everything_sp$gps_habitat=='not_assigned']<-4
output_with_everything_sp$gps_habitat_num[is.na(output_with_everything_sp$gps_habitat_num)]<-5


output_with_everything_sp$habitat_sim_arg_centre_num[output_with_everything_sp$habitat_sim_arg_centre=='high_change']<-1
output_with_everything_sp$habitat_sim_arg_centre_num[output_with_everything_sp$habitat_sim_arg_centre=='intermediate']<-2
output_with_everything_sp$habitat_sim_arg_centre_num[output_with_everything_sp$habitat_sim_arg_centre=='low_change']<-3
output_with_everything_sp$habitat_sim_arg_centre_num[output_with_everything_sp$habitat_sim_arg_centre=='not_assigned']<-4
output_with_everything_sp$habitat_sim_arg_centre_num[is.na(output_with_everything_sp$habitat_sim_arg_centre)]<-5


output_with_everything_sp$ctmm_predicted_habitat_num[output_with_everything_sp$ctmm_predicted_habitat=='high_change']<-1
output_with_everything_sp$ctmm_predicted_habitat_num[output_with_everything_sp$ctmm_predicted_habitat=='intermediate']<-2
output_with_everything_sp$ctmm_predicted_habitat_num[output_with_everything_sp$ctmm_predicted_habitat=='low_change']<-3
output_with_everything_sp$ctmm_predicted_habitat_num[output_with_everything_sp$ctmm_predicted_habitat=='not_assigned']<-4
output_with_everything_sp$ctmm_predicted_habitat_num[is.na(output_with_everything_sp$ctmm_predicted_habitat)]<-5

output_with_everything_sp$most.present.habitat_ctmm_sim_num[output_with_everything_sp$most.present.habitat_ctmm_sim=='high_change']<-1
output_with_everything_sp$most.present.habitat_ctmm_sim_num[output_with_everything_sp$most.present.habitat_ctmm_sim=='intermediate']<-2
output_with_everything_sp$most.present.habitat_ctmm_sim_num[output_with_everything_sp$most.present.habitat_ctmm_sim=='low_change']<-3
output_with_everything_sp$most.present.habitat_ctmm_sim_num[output_with_everything_sp$most.present.habitat_ctmm_sim=='not_assigned']<-4


par(mfrow=c(2,2))

#GPS
plot(st_p, border=NA)
plot(st_geometry(Cur_sp), border=grey(0.8), col=clrs_map[Cur_sp$habitat_num],add=T)
plot(output_with_everything_sp,pch='.',cex=4,col=clrs[output_with_everything_sp$gps_habitat_num],add=TRUE)


#Argos
plot(st_p, border=NA)
plot(st_geometry(Cur_sp), border=grey(0.8), col=clrs_map[Cur_sp$habitat_num],add=T)
plot(output_with_everything_sp,pch='.',cex=4,col=clrs[output_with_everything_sp$habitat_sim_arg_centre_num],add=TRUE)

#CTMM
plot(st_p, border=NA)
plot(st_geometry(Cur_sp), border=grey(0.8), col=clrs_map[Cur_sp$habitat_num],add=T)
plot(output_with_everything_sp,pch='.',cex=4,col=clrs[output_with_everything_sp$ctmm_predicted_habitat_num],add=TRUE)

#most likely habitat
plot(st_p, border=NA)
plot(st_geometry(Cur_sp), border=grey(0.8), col=clrs_map[Cur_sp$habitat_num],add=T)
plot(output_with_everything_sp,pch='.',cex=4,col=clrs[output_with_everything_sp$most.present.habitat_ctmm_sim_num],add=TRUE)


##FIGURE 6A. 
#The proportion of habitats visited by the GPS-tagged Black-tailed Godwit, as revealed from the locations from a reference GPS transmitter (small red asterisk) and from (simulated) Argos Doppler locations using the three tested approaches: raw Argos (filled grey dots), SSM (filled white dots), and most likely habitat (red dots with blue fill). The result is obtained during one iteration of the bootstrap procedure. The blue box-whisker plots represent the distribution of proportions of each habitat among the locations in the simulated Argos track, as revealed by the most likely habitat approach.

load(paste0("D:\\...\\", Files[1]))

HC<-as.data.frame(output_with_everything$ctmm_simulation_high_change)/100
   names(HC)<-'number'
   HC$habitat<-'high_change'
   Int<-as.data.frame(output_with_everything$ctmm_simulation_intermediate)/100
   names(Int)<-'number'
   Int$habitat<-'intermediate'
   LC<-as.data.frame(output_with_everything$ctmm_simulation_low_change)/100
   names(LC)<-'number'
   LC$habitat<-'low_change'
   NAss<-as.data.frame(output_with_everything$ctmm_simulation_not_assigned)/100
   names(NAss)<-'number'
   NAss$habitat<-'not_assigned'
for_boxplot_sim<-rbind(HC, Int,LC,NAss)


boxplot(number~as.factor(habitat),for_boxplot_sim,col = 'darkseagreen1', medcol = 'grey', boxlty = 0, pch='.')


argos_output<-as.data.frame(c(as.vector(table(output_with_everything$ habitat_sim_arg_centre))/1819))
names(argos_output)<-'number'
habitat<-c('high_change', 'intermediate', 'low_change','not_assigned')
argos_output<-cbind(argos_output,habitat)
stripchart(number ~ habitat,
           data = argos_output,
           #method = "jitter",
           pch = 19,
		   cex=2,
           #col = 2:4,
		   col=grey(0.5),
           vertical = TRUE,
           add = TRUE)

ctmm_output<-as.data.frame(c(as.vector(table(output_with_everything$ ctmm_predicted_habitat))/1819))
names(ctmm_output)<-'number'
habitat<-c('high_change', 'intermediate', 'low_change','not_assigned')
ctmm_output<-cbind(ctmm_output,habitat)
stripchart(number ~ habitat,
           data = ctmm_output,
           #method = "jitter",
           pch = 21,
		   cex=2,
           #col = 2:4,
		   bg='white',
		   col=grey(0.5),
           vertical = TRUE,
           add = TRUE)
		   
		   
ML_output<-as.data.frame(c(as.vector(table(output_with_everything$ most.present.habitat_ctmm_sim))/1819))
names(ML_output)<-'number'
habitat<-c('high_change', 'intermediate', 'low_change','not_assigned')
ML_output<-cbind(ML_output,habitat)
stripchart(number ~ habitat,
           data = ML_output,
           #method = "jitter",
            pch = 21,
		  cex=2,
           #col = 2:4,
		   col='red',
		   bg='darkseagreen1',
		   lwd=3,
		   vertical = TRUE,
           add = TRUE)   
		   
gps_output<-as.data.frame(c(as.vector(table(output_with_everything$gps_habitat))/1819))
names(gps_output)<-'number'
habitat<-c('high_change', 'intermediate', 'low_change','not_assigned')
gps_output<-cbind(gps_output,habitat)
stripchart(number ~ habitat,
           data = gps_output,
           #method = "jitter",
           #pch = 25,
		    pch = '*',
		   cex=2,
           #col = 2:4,
		   col='red',
		   bg='2',
		   lwd=2,
		   vertical = TRUE,
           add = TRUE)

	
##FIGURE 6B. 
#The proportion of location points in a 100-iteration bootstrap procedure, for which habitat types coincided with habitat types assigned based on the GPS reference locations. 

All_out<-c()

for (file in 1:length(Files)) {
cat(file, '\r')	

load(paste0("D:\\...", Files[file]))

output_with_everything<-output_with_everything[!is.na(output_with_everything$gps_habitat),]

output_with_everything$coincide_gps_arg_centre<-0
output_with_everything$coincide_gps_ctmm<-0
output_with_everything$coincide_gps_ctmm_most_likely_habitat<-0

output_with_everything$coincide_gps_arg_centre[output_with_everything$gps_habitat==output_with_everything$habitat_sim_arg_centre & !is.na(output_with_everything$gps_habitat)]<-1
output_with_everything$coincide_gps_ctmm[output_with_everything$gps_habitat==output_with_everything$ctmm_predicted_habitat & !is.na(output_with_everything$gps_habitat)]<-1
output_with_everything$coincide_gps_ctmm_most_likely_habitat[output_with_everything$gps_habitat==output_with_everything$most.present.habitat_ctmm_sim & !is.na(output_with_everything$gps_habitat)]<-1

		   All_out<-rbind(All_out, c('coincide_gps_arg_centre',sum(output_with_everything$coincide_gps_arg_centre),nrow(output_with_everything)),
		   c('coincide_gps_ctmm',sum(output_with_everything$coincide_gps_ctmm),nrow(output_with_everything)),
		   c('coincide_gps_ctmm_most_likely_habitat',sum(output_with_everything$coincide_gps_ctmm_most_likely_habitat),nrow(output_with_everything)))	   
		     
}


All_out<-as.data.frame(All_out)
str(All_out)
 names(All_out)<-c('method','coincidence_rate','nr_noNA_fixes')
All_out$coincidence_rate<-as.numeric(All_out$coincidence_rate)
All_out$nr_noNA_fixes<-as.numeric(All_out$nr_noNA_fixes)
All_out$coincidence_rate_prop<-All_out$coincidence_rate/All_out$nr_noNA_fixes
All_out$method_index[All_out$method=='coincide_gps_arg_centre']<-'Argos location'
All_out$method_index[All_out$method=='coincide_gps_ctmm']<-'ctmm location'
All_out$method_index[All_out$method=='coincide_gps_ctmm_most_likely_habitat']<-'ML habitat'

#Plot the coinidence rate (FIGURE 6B)
plot(All_out$coincidence_rate_prop~as.factor(All_out$method_index),ylab='Rate of coincidence with GPS habitat assignments', xlab='', boxlty = 0, ylim=c(0,1))

```